---
title: "Multi-environment Knockoff Filter examples"
output: html_notebook
---

We demonstrate the usage of the functions here. 

```{r}
source("MEKF/multienv.R")
source("MEKF/accumulation_test.R")
source("MEKF/importance_stats.R")
```

We start by generating a small dataset. 
```{r}
set.seed(1)
n = 100 ## number of observations
p = 50 ## number of variables
k = 20 ## number of nonnulls
num_env = 4 ## number of environments
amplitude = 5
rhos = rep(0,10)
nonnulls = sample(1:p, k)
beta = matrix(rep(0,num_env*p), nrow = p)
for (i in 1:num_env){
    beta[nonnulls, i] = 1
}
beta = beta* amplitude / sqrt(n)

## generate X and Y from a linear model
Xs = list()
ys = list()
for (i in 1:num_env){
    X = matrix(rnorm(n*p),n)
    Xs[[i]] = X
    y = X %*% beta[,i] + rnorm(n)
    ys[[i]] = y
}
```

We construct knockoffs seperately for each environment 
```{r}
X_ks = list()
for (i in 1:num_env){
    X_ks[[i]] = create.gaussian(X, rep(0,p), toeplitz(rhos[i]^(0:(p-1))))
}
```

### MEKF with meta-analysis statistics

We compute knockoff statistics seperately for each environment
```{r}
W_matrix = NULL
for (i in 1:num_env){
    W = stat.lasso_coefdiff(Xs[[i]], X_ks[[i]], ys[[i]])
    W_matrix = cbind(W_matrix,W)
}
```

We run MEKF to test consistent conditional associations and partially consistent conditional associations.
```{r}
## Consistency testing
invariant_model(W_matrix)
## Parital consistency testing (Selective Seqstep+)
partial_conjunction(W_matrix, r = 2)
## Parital consistency testing (Accumulation test)
partial_conjunction(W_matrix, r = 2, method = "accumulation")
```

### MEKF with cross-prior statistics
We compute cross-prior statistics and test consistent conditional associations
```{r}
W_matrix = compute_stats_with_prior(Xs, X_ks, ys)
invariant_model(W_matrix)
```

### Transfer learning with knockoffs
We run multi-environment knockoff filter for transfer learning. Note that the first environment is treated as the target environment.
```{r}
W_trans = compute_transfer_stats_with_prior(Xs, X_ks, ys)
thres_trans = knockoff.threshold(W_trans)
which(W_trans >= thres_trans)
```

